BlogForever Crawler: Techniques and Algorithms\\to Harvest Modern Weblogs

### 2013-12-03 tex/3-algorithms.tex
3.2 fixed.

\TODO{When I read this section for the first time, I was confused.
After I also read 3.3 and 3.4 I understood better.
You should have a nicely structured overview of the algorithm in 3.2 and have references for 3.3 and 3.4
When you describe the algorithm overview, you should say explicitly that function X and operation Y is explained in section Z, etc}

@@

% In the case the reader does not know how to read pseudocode
Algorithm \ref{extractionAlgo} show the generic procedure we use to build extraction rules. The idea is quite simple: for each \code{(}\emph{page, target}\code{)} input, compute out of all extraction rules the best one with respect to a certain \code{ScoreFunction}. The rule which was the most frequently a \emph{best rule} is then returned.

@@

% abs, plan
Most functions in algorithm \ref{extractionAlgo} are voluntarily abstract at this point and will be explained in details in the remaining of this section. \ref{extractionrulesandstringsimilarity}, \ref{timecomplexityandlinearreformulation}, \ref{variationsforauthorsdatesandcomments}

% general idea, embarrassingly parallel
\TODO{This paragraph is not clear.}
The idea is quite simple: to compute the best extraction rule for each pair of HTML pages and target content and to finally return the most frequent best rule. Making each of these computations independent might seem like a loss of information compared to alternative solutions such as having a global score for each rule, computed as the average of each rule's score over all the pages of the feed. In our experimentation we observed several cases where the independent solution performs better\TODO{example, reference or proof?}. When web feeds have posts with very short content, mean based solutions tend to be more influenced by these outliers and are inclined to return erroneous rules which fail to return target contents but constantly have an average score.\TODO{rephrase!}

In addition, having an independent computation for each input makes the algorithm \emph{embarrassingly parallel}: iterations of the outer loop can trivially be executed by multiple threads.

>>>>

@@

% textual pseudocode
Algorithm \ref{extractionAlgo} show the generic procedure we use to build extraction rules. The idea is quite simple: for each \code{(}\emph{page, target}\code{)} input, compute out of all extraction rules the best one with respect to a certain \code{ScoreFunction}. The rule which was the most frequently a \emph{best rule} is then returned.

@@

% Embarrassingly parallel
One might notice that each \emph{best rule} computation is independent and operates on a different input pairs. Therefore algorithm \ref{extractionAlgo} \emph{embarrassingly parallel}: iterations of the outer loop can trivially be executed by multiple threads.

% abs, plan
Functions in algorithm \ref{extractionAlgo} are voluntarily abstract at this point and will be explained in details in the remaining of this section. \ref{extractionrulesandstringsimilarity} defines \code{AllRules}, \code{Apply} and the \code{ScoreFunction} we use for article and title extraction. In \ref{timecomplexityandlinearreformulation} we analyses time complexity of Algorithm \ref{extractionAlgo} and give a linear time reformulation using dynamic programing. Finally, \ref{variationsforauthorsdatesandcomments} shows how the \code{ScoreFunction} can be adapted to extract authors, dates and comments.
